---
title: 'Social Status, Language Use, and Context: Insights from Lexical Entrainment'
author: "Greta Gandolfi"
date: "21.09.2022"
output:
  html_document:
    df_print: paged
---

First, I import all the packages I need.
```{r echo=TRUE, message=FALSE, warning=FALSE}
#import all the packages
library(ggsignif)
library(lme4)
library(MASS)
library(lmerTest)
library(Rmisc)
library(ggplot2)
library(plyr)
library(gdata)
library(sjPlot)
library(dplyr)
library(effects)
library(sjPlot)
library(lattice)
library(psych)
library(knitr)
library(sjmisc)
library(sjlabelled)
library(tidyr)
library(effects)
```
Then I import an anonymised version of the dataset. 
Here are my dataset variables: 
- "disfavoured.word": target stimuli (n=32), e.g. "seat"
- "response.lower": response provided by participants, lower case, e.g. "seat" or "chair"
- "entrained": 1 or 0 (1 means that, in the naming trial, participants repeated what their "interlocutor" produced in the matching trial)
- "interlocutor.SES": interlocutor social economic status ("high" or "low")
- "session.order": the experiment included two sessions of the matching/naming task (1st or 2nd)
- "set": stimuli were divided into two sets (1 or 2) 
- "group": participants were assigned to two groups (prime: i.e., rating then task group and no prime: i.e., the task then rating group)
- "participantID": random anonymised alphanumeric code associated with participants
- "stimuli.order": order of stimuli presentation (1 to 16)
- "f": "disfavoured.word" frequency in the norming task (spontaneous naming) (value between 0 and 1)
- "experiment": experiment 1 or 2

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
#import data
d0 <- read.csv("social-status-experiments.csv") 
d0$participantID <- as.factor(as.character(d0$prolific_id))
d0$interlocutor.SES <- as.factor(as.character(d0$condition))
d0$stimuli.order <- as.factor(as.character(d0$randomBlock))
d0$gender.participant <- as.factor(d0$gender_participant)
d0$f <- as.factor(d0$f1)
d0$rating.position <- as.factor(as.character(d1$group))
d0 <- d0 %>% 
  mutate(rating.position = if_else(rating.position == "prime", "rating, then main task", "main task, then rating"))
 

#count the excluded participants
participants.count <- d0 %>%
  dplyr::group_by(experiment) %>%
  dplyr::summarise(N = n()/32)

participants.excluded.exp1 <- 100-(participants.count$N[1]*100/240)
participants.excluded.exp2 <- 100-(participants.count$N[2]*100/480)
```

We excluded participants that failed the manipulation check, i.e. `r participants.excluded.exp1`% in the first experiment and `r  participants.excluded.exp2`% in the second experiment.

### Analysis
**Do pariticipants entrain?**

```{r message=FALSE, warning=FALSE}
#EXP1
entrainbyitem_total.exp1 <- d0 %>%
  filter(experiment == "experiment 1") %>%
  dplyr::group_by(disfavoured.word, f) %>%
  dplyr::summarise(entrainbyitem = sum(as.numeric(as.character(entrained)), na.rm = TRUE)/participants.count$N[1])

wt.exp1 <- wilcox.test(as.numeric(entrainbyitem_total.exp1$f), 
            as.numeric(entrainbyitem_total.exp1$entrainbyitem), 
            paired=TRUE, 
            exact = FALSE)
#EXP2
entrainbyitem_total.exp2 <- d0 %>%
  filter(experiment == "experiment 2") %>%
  dplyr::group_by(disfavoured.word, f) %>%
  dplyr::summarise(entrainbyitem = sum(as.numeric(as.character(entrained)), na.rm = TRUE)/participants.count$N[1])

wt.exp2 <- wilcox.test(as.numeric(entrainbyitem_total.exp2$f), 
            as.numeric(entrainbyitem_total.exp2$entrainbyitem), 
            paired=TRUE, 
            exact = FALSE)
#any(entrainbyitem_total.exp2$f>entrainbyitem_total.exp2$entrainbyitem) to understand what V=0 means.
```

Yes, in both the experiments. `f` corresponds to the frequency of the word (here in `disfavoured.word`) in the norming task (spontaneous naming). Participants were asked to answer the question *“What is the first word you would use to name this object?"*, where *"this object"* referred to a picture they could see on the same page, while  `entrainbyitem` corresponds to the frequency of the word in the picture naming picture matching task. In the norming task (spontaneous naming), words in  `disfavoured.word` were used `r round(mean(entrainbyitem_total.exp2$f)*100, digits=2)`% of the trials. While, in the picture naming tasks, words in `disfavoured.word` were used `r round(mean(entrainbyitem_total.exp1$entrainbyitem)*100, digits=2)`% of trials in experiment 1 (p<.001) and `r round(mean(entrainbyitem_total.exp1$entrainbyitem)*100, digits=2)`% of trials in experiment 2 (p<.001).

----

**Do participants entrain more often with high status interlocutors?**
```{r}
#number of repetitions per participant 
d.exp1 <- d0 %>%
  filter(experiment == "experiment 1")

f.1=ftable(d.exp1$interlocutor.SES, d.exp1$entrained)

# percentage of repetitions/non-repetitions per condition
round(100*prop.table(f.1, 1), digits = 2)
```
In experiment 1, participants entrained with high social status interlocutors on `r round(100*prop.table(f.1, 1), digits = 2)[3]`% of the trials and with low social status interlocutors on `r round(100*prop.table(f.1, 1), digits = 2)[4]`% of the trials.

```{r}
#number of repetitions per participant 
d.exp2 <- d0 %>%
  filter(experiment == "experiment 2")

f.2=ftable(d.exp2$group, d.exp2$interlocutor.SES, d.exp2$entrained)

# percentage of repetitions/non-repetitions per condition
round(100*prop.table(f.2, 1), digits = 2)
```
In experiment 2, participants entrained with high social status interlocutors on `r round(100*prop.table(f.2, 1), digits = 2)[5]`% of the trials and with low social status interlocutors on `r round(100*prop.table(f.2, 1), digits = 2)[6]`% of the trials. However, if they were asked to rate the social status of their interlocutor before the main task, they entrained respectively on `r round(100*prop.table(f.2, 1), digits = 2)[7]`% of the trials and `r round(100*prop.table(f.2, 1), digits = 2)[8]`% of the trials. 

---

**Is any difference statistically significant?**
```{r}
contrasts(d.exp1$interlocutor.SES) <- c(0.5,-0.5) # changed contrast to effect coding

m0.1 <- glmer(entrained~1+(1+interlocutor.SES|participantID)+(1+interlocutor.SES|disfavoured.word), data =d.exp1, family ="binomial")
summary(m0.1)$varcor #(1+interlocutor.SES|disfavoured.word) corr=1
m0.1.1 <- glmer(entrained~1+(1+interlocutor.SES|participantID)+(1|disfavoured.word), data =d.exp1, family ="binomial")
summary(m0.1.1)$varcor
m1.1 <- glmer(entrained~interlocutor.SES+(1+interlocutor.SES|participantID)+(1|disfavoured.word), data =d.exp1, family ="binomial")
anova(m0.1.1,m1.1) #adding the interlocutor.SES doesn't really explain the data better thn m0.1.1

summary(m1.1)
plot_model(m1.1)
```

```{r}
contrasts(d.exp2$interlocutor.SES) <- c(0.5,-0.5) 
contrasts(d.exp2$group) <- c(-0.5,0.5) 
contrasts(d.exp2$session.order) <- c(0.5,-0.5) 

m0.2 <- glmer(entrained ~ 1 +(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")
m1.2 <- glmer(entrained ~ interlocutor.SES +(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")
m2.2 <- glmer(entrained ~ interlocutor.SES*group +(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")
#m3.2 <- glmer(entrained ~ interlocutor.SES*group*session.order+(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial") failed to converge
m3.2 <- glmer(entrained ~ interlocutor.SES*group+session.order+(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")

anova(m0.2,m1.2,m2.2,m3.2)

summary(m3.2)
plot_model(m3.2)
#plot(allEffects(m3.2))
```
In Experiment 1, participants seem to align to high and low social status interlocutors to the same extent  (p = .09). Interestingly, Experiment 2 revealed an interaction between the rating question position and interlocutors’ social status (p < .01): participants who were asked to rate the social status of their interlocutor before the main task were more likely to entrain with their high social status interlocutor than with their low social status interlocutor, while participants who were asked to rate their interlocutor social status after the main task entrained to a similar extent (25% of trials) with high and low social status interlocutors, thus replicating Experiment 1 results. In both the experiments, participants entrained more often in the first than in the second session (p < .01). 

### Visualisation
**Main Findings**
```{r echo=TRUE, message=FALSE, warning=FALSE}
#grouping the data 
vis0 <- d0 %>%
  dplyr::group_by(experiment, interlocutor.SES, group) %>%
  dplyr::summarise(entrainment.m = mean(entrained)*100,
                   entrainment.sd = sd(entrained)*100,
                   N = n(),
                   entrainment.se = entrainment.sd/sqrt(n()))


ggplot(vis0, aes(x=group, y=entrainment.m, fill=interlocutor.SES)) +
  labs(title="Does interlocutors' social status modulate lexical entrainment?", subtitle="Yes, but only when participants rate the social status of their interlocutor before the main task", y="proportion of lexical entrainment (%)", x="rating position") +
  ylim(0, 50) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
  plot.subtitle = element_text(hjust = 0.5)) +
  scale_fill_manual(values=c("#333399", "#d0d2ef"), name = "social status", labels = c("high", "low")) +
  facet_grid(cols=vars(experiment)) +
  geom_bar(stat = "identity",position = "dodge", width = .5, alpha=.6) +
  theme(legend.position="bottom") +
  geom_errorbar(aes(ymax=entrainment.m+entrainment.se,ymin=entrainment.m-entrainment.se, width=.2), position=position_dodge(.5)) 
  
#ggsave("plot-amlap-bar.jpg", width = 8, height = 6)
```

---

**Additional findings: Session Order**
```{r echo=TRUE, message=FALSE, warning=FALSE}
vis1 <- d0 %>%
  dplyr::group_by(experiment, session.order) %>%
  dplyr::summarise(entrainment.m = mean(entrained)*100,
                   entrainment.sd = sd(entrained)*100,
                   N = n(),
                   entrainment.se = entrainment.sd/sqrt(n()))

ggplot(vis1, aes(x=experiment, y=entrainment.m, fill=session.order)) +
  labs(y="proportion of lexical entrainment (%)", x="experiment") +
  ylim(0, 50) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values=c("#dbedef", "#2aa6af"), name="session order", labels =c("first", "second")) +
  geom_bar(stat = "identity",position = "dodge", width = .5, alpha=.6) +
   theme(legend.position="bottom") +
  geom_errorbar(aes(ymax=entrainment.m+entrainment.se,ymin=entrainment.m-entrainment.se, width=.2), position=position_dodge(.5)) 
#ggsave("plot-order-amlap-bar.jpg", width = 5, height = 5)


m0.3 <-  glmer(entrained~session.order*experiment+(1|participantID)+(1|disfavoured.word), data =d0, family ="binomial")
summary(m.session)
#plot(allEffects(m.session))
```

**Additional findings: stimuli order**
Visualisation
```{r echo=TRUE, message=FALSE, warning=FALSE}
v2 <- d.exp2  %>%
  dplyr::group_by(stimuli.order, interlocutor.SES, group) %>%
  dplyr::summarise(entrainment.m = mean(entrained)*100,
                   entrainment.sd = sd(entrained)*100,
                   N = n(),
                   entrainment.se = entrainment.sd/sqrt(n()))


ggplot(v2, aes(y=entrainment.m, x=stimuli.order, color=interlocutor.SES)) + 
  geom_point(position=position_dodge(.5)) + 
  geom_line() + 
  scale_color_brewer(palette = "Paired", 
                      name = "social status", 
                      labels = c("high", "low")) +
  ylim(0,50) +
  scale_x_continuous(breaks = seq(0, 16, 2)) +
  facet_wrap(vars(group)) +
  labs(y="proportion of lexical entrainment (%)", x="stimuli order") +
  geom_errorbar(aes(ymax=entrainment.m+entrainment.se,ymin=entrainment.m-entrainment.se, width=.2), position=position_dodge(.5)) +
  theme_minimal()

#ggsave("plot-stim-order-xprag-bar.png",width = 6, height = 6)
```

Model
```{r}
d.exp2$stimuli.order <- scale((d0$stimuli.order), scale=FALSE)
contrasts(d.exp2$interlocutor.SES) <- c(0.5,-0.5) 

m0.4 <- glmer(entrained ~ 1 +(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")
m1.4 <- glmer(entrained ~ interlocutor.SES +(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")
m2.4 <- glmer(entrained ~ stimuli.order*interlocutor.SES +(1+interlocutor.SES|participantID)+(1|disfavoured.word), data = d.exp2, family ="binomial")
anova(m0.4,m1.4, m2.4)
summary(m2.4)
```

** Additional findings: participants' gender **
Visualisation
```{r}
v3 <- d0 %>%
  dplyr::group_by(rating.position, social.status, experiment, gender.participant) %>%
  dplyr::summarise(entrainment.m = mean(entrained)*100,
  entrainment.sd = sd(entrained)*100,
  N = n()/15,
  entrainment.se = entrainment.sd/sqrt(n()))

ggplot(v3, aes(x=gender.participant, y=entrainment.m, fill=social.status)) +
labs(y="proportion of lexical entrainment (%)", x="participants' gender") +
ylim(0, 50) +
theme_minimal() +
scale_fill_brewer(palette = "BuPu", name = "social status", labels = c("high", "low")) +
facet_wrap(experiment ~ rating.position, drop=TRUE) +
geom_bar(stat = "identity",position = "dodge", width = .5) +
theme(legend.position="bottom") +
geom_errorbar(aes(ymax=entrainment.m+entrainment.se,ymin=entrainment.m-entrainment.se, width=.2), position=position_dodge(.5))

#ggsave("plot-gender-xprag-bar.jpg", , width = 10, height = 4)
```

Model
```{r}
contrasts(d1$interlocutor.SES) <- c(0.5,-0.5) 
contrasts(d1$gender.participant) <- c(-05,0.5)
m0.5 <- glmer(entrained ~ 1 +(1+condition|prolific_id)+(1|label), data = d1, family ="binomial")
m1.5 <- glmer(entrained ~ condition +(1+condition|prolific_id)+(1|label), data = d1, family ="binomial")
m2.5 <- glmer(entrained ~ condition*gender.participant +(1+condition|prolific_id)+(1|label), data = d1, family ="binomial")
anova(m0.5,m1.5, m2.5)
summary(m2.4)
```
